Deep mutational scanning of hemagglutinin helps predict evolutionary fates of human H3N2 influenza variants

### 2018-04-08 paper/cover_letter.tex
fixed cover letter typo noticed by Juhye

Finally, our work will be of specific interest to evolutionary biologists because it sheds light on the question of how the effects of mutations shift during evolution.
Prior work has experimentally compared the effects of mutations among closely related proteins, but ours is the first to compare them among highly diverged proteins.
We find that many mutations have different effects in H3 and H3 hemagglutinins, showing the stark effect of epistasis when comparing distant homologs.

>>>>

Finally, our work will be of specific interest to evolutionary biologists because it sheds light on the question of how the effects of mutations shift during evolution.
Prior work has experimentally compared the effects of mutations among closely related proteins, but ours is the first to compare them among highly diverged proteins.
We find that many mutations have different effects in H1 and H3 hemagglutinins, showing the stark effect of epistasis when comparing distant homologs.
